---
title: 'Project #1'
author: "Bianka Figueroa"
date: "9/19/2021"
output: html_document
---

## Background

### In this project, you’re given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:

### Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents

### For the first player, the information would be:

### Gary Hua, ON, 6.0, 1794, 1605

### 1605 was calculated by using the pre-tournament opponents’ ratings of 1436, 1563, 1600, 1610, 1649, 1663, 1716, and dividing by the total number of games played.

### Setting up the Directory


```{r, warning=FALSE, include=T}

setwd("C:/Users/BFigueroa/OneDrive - City University of New York/SPS/DATA MANAGEMENT/Projects/Project 1")

require(data.table)
require(readr)
require(tidyverse)
```

### Read the text file into R


```{r, warning=FALSE, include=T}

tournament <- read_lines("tournamentinfo.txt", skip = 1)
head(tournament)

```

### Remove "-" 


```{r, warning=FALSE, include=T}
chess <- str_remove_all(tournament, "-")
head(chess)

```

### Remove empty rows


```{r, warning=FALSE, include=T}
chess <- as.data.frame(chess)
head(chess)

chess <- data.frame(chess[!apply(chess == "", 1, all),])
head(chess)
tail(chess)

chess <- chess[c(3:130),]
head(chess)

```

### Getting Player's Name


```{r warning=FALSE, include=T}

player_name <- "([[:upper:]]+\\s){2,}"
name <- unlist(str_extract_all(unlist(chess),player_name))
str_trim(name, side = "right")

name <- data.frame(name)
head(name)

name <- name[c(2:65),]
head(name)

```

### Getting Player's State

```{r, warning=FALSE, include=T}
state_name <- "([[:upper:]]){2}\\s(?=\\|)"
state <- unlist(str_extract_all(unlist(chess), state_name))
str_trim(state, side = "right")
```

### Total Number of Points

```{r, warning=FALSE, include=T}
total_points <- "\\d\\.\\d"
points <- unlist(str_extract_all(unlist(chess), total_points))
points
```
### Player’s Pre-Rating

```{r, warning=FALSE, include=T}
pre_rating <- "(?<!\\>\\s)(?<=\\s{1,2}|\\s\\:)(\\d{3,4}(?=\\s|P))"
pre <- unlist(str_extract_all(unlist(chess), pre_rating))
pre <- str_trim(pre, side = "right")
pre
```
### Average Pre Chess Rating of Opponents

```{r, warning=FALSE, include=T}
opponents_rating <- "(\\d{1,}|[[:blank:]]{1})(?=\\|)"
player_opponents <- unlist(str_extract_all(unlist(chess), opponents_rating))

player_opponents[player_opponents == " "]  <- NA
head(player_opponents)

opponent1 <- as.numeric(player_opponents[seq(4, length(player_opponents), 10)])
opponent1 <- as.numeric(opponent1[seq(1, length(opponent1), 2)])
opponent2 <- as.numeric(player_opponents[seq(5, length(player_opponents), 10)])
opponent2 <- as.numeric(opponent2[seq(1, length(opponent2), 2)])
opponent3 <- as.numeric(player_opponents[seq(6, length(player_opponents), 10)])
opponent3 <- as.numeric(opponent3[seq(1, length(opponent3), 2)])
opponent4 <- as.numeric(player_opponents[seq(7, length(player_opponents), 10)])
opponent4 <- as.numeric(opponent4[seq(1, length(opponent4), 2)])
opponent5 <- as.numeric(player_opponents[seq(8, length(player_opponents), 10)])
opponent5 <- as.numeric(opponent5[seq(1, length(opponent5), 2)])
opponent6 <- as.numeric(player_opponents[seq(9, length(player_opponents), 10)])
opponent6 <- as.numeric(opponent6[seq(1, length(opponent6), 2)])
opponent7 <- as.numeric(player_opponents[seq(10, length(player_opponents), 10)])
opponent7 <- as.numeric(opponent7[seq(1, length(opponent7), 2)])
player_opponents <- matrix(c(opponent1, opponent2, opponent3, opponent4, opponent5, opponent6, opponent7),nrow = 64, ncol = 7)
head(player_opponents)

ID_number <- "\\d{1,2}(?=\\s\\|)"
ID <- unlist(str_extract_all(unlist(chess), ID_number))

chess_avg <- 0
chess_table <- 0

for (i in 1:(length(ID)))
{
  chess_avg[i] <- mean(as.numeric(pre[player_opponents[i,]]), na.rm = T)
}
```
## Putting all the information together in a new table

```{r, warning=FALSE, include=T}

chess_table <- data.frame(name, state, points, pre, chess_avg)
chess_table

```
## Rounding the chess_average column

```{r, warning=FALSE, include=T}
avg_round <- round(chess_avg, digits = 0)
avg_round

chess_final <- data.frame(name, state, points, pre, avg_round)
chess_final

head(chess_table)
head(chess_final)
```
## Rename table columns

```{r, warning=FALSE, include=T}
names(chess_final)[1] <- "Player's Name"
names(chess_final)[2] <- "State"
names(chess_final)[3] <- "Total Points"
names(chess_final)[4] <- "Pre Rating"
names(chess_final)[5] <- "Avg Pre Rating"

head(chess_final)
```
## Save file as .csv

```{r, warning=FALSE, include=T}
write.csv(chess_final, file = "tournament.csv")
```




